Adaption of the Chumbley Score to matching of bullet striation marks

### 2018-04-24 doc/paper.Rmd
couple more CS1 results

errorsCV <- rbind(errorsCV1, errorsCV2)

errorsCV %>% 
  ggplot(aes(x = wo, y = beta, colour=factor(alpha))) + 
  geom_point(aes(shape=factor(wv)), size=2.5) +
  geom_smooth(aes(group=alpha), se=FALSE, method="loess", span=1,  size=.7) +
  theme_bw() +
  scale_colour_brewer(expression("Nominal\ntype I error"~alpha),
                      palette="Set2") +
  scale_shape_discrete(expression("Size of\nvalidation window "~w[v])) +
  xlab(expression("Window size for optimization "~w[o])) +
  ylab("Type II error rate") +
  facet_wrap(~method, labeller="label_both")

>>>>

errorsCV <- rbind(errorsCV1, errorsCV2)
errorsCV %>% 
  ggplot(aes(x = wo, y = beta, colour=factor(alpha))) + 
  geom_point(aes(shape=factor(wv)), size=2.5) +
  geom_smooth(aes(group=alpha), se=FALSE, method="loess", span=1,  size=.7) +
  theme_bw() +
  scale_colour_brewer(expression("Nominal\ntype I error"~alpha),
                      palette="Set2") +
  scale_shape_discrete(expression("Size of\nvalidation window "~w[v])) +
  xlab(expression("Window size for optimization "~w[o])) +
  ylab("Type II error rate") +
  facet_wrap(~method, labeller="label_both")
